### 2019-04-02 papers/journal/intro.tex
Made the sections uniform: Every subcategory of a subsection is now a subsubsection. The BIO outline Is now similar to CS

\subsection{The model}
The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed.
\item Each compartment is in steady state, gain and loss of the molecules is balance.
\item Molecules are neither created nor destroyed.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
\item An active SNARE pair is necessary and sufficient for fusion. 
\end{enumerate}
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

>>>>

\subsection{The model}
\todo{Ankit: The Rothman model has no intuition; Add couple of lines relating it to VTS; Also, relate it to previous subsection. The connect is lacking.} The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed.
\item Each compartment is in steady state, gain and loss of the molecules is balance\todo{Ankit: Need intuition and also reasoning why this is okay to add this as an assumption}.
\item Molecules are neither created nor destroyed.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
\item An active SNARE pair is necessary and sufficient for fusion. 
\end{enumerate}

\todo{Ankit: Need some additional discussion;4 lines max about the legitamecy of the assumptions.}
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
